Your Substantive Title Here

### 2024-01-11 Documents/Paper.qmd
added names to report

---
title: "Your Substantive Title Here"
author: 
  - Your Name1^[American University]
  - Your Name2^[American University]
format: 
  pdf:
    number-sections: true
    toc: false
    geometry: 
      - top=3cm
date: 2023-09-27
date-format: iso
documentclass: article
editor: source
abstract: "This is our informative abstract of fewer than 200 words. It describes what we investigate, how we investigate it, and what we find."
bibliography: main.bib
---

>>>>

---
title: "Your Substantive Title Here"
author: 
  - Melanie Klein^[American University]
  - Michael Taffe^[American University]
  - Ramiro Arevalo^[American University]

format: 
  pdf:
    number-sections: true
    toc: false
    geometry: 
      - top=3cm
date: 2023-09-27
date-format: iso
documentclass: article
editor: source
abstract: "This is our informative abstract of fewer than 200 words. It describes what we investigate, how we investigate it, and what we find."
bibliography: main.bib
---
